---
title: "Medians Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Medians Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Medians Examples

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

Each section of examples below progresses from more complete input to less complete input, moving from miminal required inference to maximal inference on the part of the function. Similarly, the structure highlights the flexibility of the function across diverse study designs and input constraints.

### One Sample Cases

```{r}
# 1. Direct median with SE and sample size (assumes t-distribution)
backcalc_medians(m = 25.4, se = 2.1, n = 30)

# 2. Median with IQR and sample size (SE approximated from IQR, assumes normality)
backcalc_medians(m = 25.4, sd = 10, n = 30)

# 3. Median with confidence interval and sample size (SE inferred from CI)
backcalc_medians(m = 30, ci = c(25, 35), n = 25)

# 4. Median with p-value and degrees of freedom (statistic and SE inferred)
backcalc_medians(m = 2.5, p = 0.03, df = 29)

# 5. Median with p-value and sample size (df inferred, SE and statistic approximated)
backcalc_medians(m = 2.1, p = 0.05, n = 16)
```

### Two Sample Cases

```{r}
# 6. Two group medians, IQRs, and ns provided (difference computed, SE and df inferred)
backcalc_medians(m = c(15, 12), sd = c(4, 5), n = c(40, 35))

# 7. Median difference and SE provided (CI and p-value inferred)
backcalc_medians(m = c(15, 12), se = 1.5, n = c(40, 35))

# 8. Medians and p-value + df provided (infer SE and statistic)
backcalc_medians(m = c(10, 7), p = 0.04, df = 50)

# 9. Medians and confidence interval provided (infer SE)
backcalc_medians(m = c(100, 90), ci = c(2, 18), n = c(50, 45))

# 10. Medians and IQRs provided, but only n for one group (partial inference possible)
backcalc_medians(m = c(8, 5), sd = c(3, 4), n = 20)
```

### Insufficient Information Cases

```{r}
# 11. No median, SE, p, or CI provided (should warn)
backcalc_medians(n = 15)

# 12. Median and IQR provided, but no n (cannot infer SE)
backcalc_medians(m = 7, sd = 2)

# 13. Only p-value and df provided (no median or SE; insufficient)
backcalc_medians(p = 0.05, df = 20)

# 14. Median and df provided, but no SE, p, or CI
backcalc_medians(m = 5.6, df = 10)

# 15. Only test statistic and df provided (no median or SE; insufficient)
backcalc_medians(statistic = 2.5, df = 18)
```
