---
title: "Proportions Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Proportions Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Proportions Examples

Each section of examples below progresses from more complete input to less complete input, moving from miminal required inference to maximal inference on the part of the function. Similarly, the structure highlights the flexibility of the function across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### One Sample Cases

```{r}
# 1. Least inference: Provide proportion and sample size only
backcalc_props(prop = 0.4, n = 100)

# 2. Provide count and sample size, infer proportion and SE
backcalc_props(x = 45, n = 120)

# 3. Provide proportion, sample size, and test statistic (z)
backcalc_props(prop = 0.5, n = 150, statistic = 2.1)

# 4. Provide proportion, sample size, and p-value, infer SE and statistic
backcalc_props(prop = 0.35, n = 80, p = 0.04)

# 5. Provide proportion, t-statistic, and degrees of freedom, infer SE and p
backcalc_props(prop = 0.6, statistic = 2.2, df = 19)
```

### Two Sample Cases

```{r}
# 6. Least inference: Provide two proportions and sample sizes only
backcalc_props(prop = c(0.55, 0.4), n = c(150, 130))

# 7. Provide two proportions, sample sizes, and test statistic (z)
backcalc_props(prop = c(0.6, 0.5), n = c(120, 110), statistic = 2.2)

# 8. Provide two proportions, sample sizes, and p-value, infer SE and statistic
backcalc_props(prop = c(0.3, 0.35), n = c(100, 110), p = 0.05)

# 9. Provide counts and sample sizes for two groups, infer difference and SE
backcalc_props(x = c(40, 30), n = c(100, 90))

# 10. Provide two proportions, p-value, and degrees of freedom (t-test)
backcalc_props(prop = c(0.45, 0.5), p = 0.04, df = 50)
```

### Insufficient Information Cases

```{r}
# 11. No prop, no counts, no SE — cannot infer
backcalc_props()

# 12. Provide statistic and sample size only, no prop or se — infer prop and SE
backcalc_props(statistic = 2.1, n = 50)

# 13. Provide n only, no prop, counts, or se
backcalc_props(n = 100)

# 14. Provide counts but missing sample size
backcalc_props(x = 30)

# 15. Provide CI but no counts or proportion — cannot compute estimate or SE
backcalc_props(ci = c(0.2, 0.8))
```
