---
title: "Ratios Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Ratios Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Ratios Examples

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

Each section of examples below progresses from more complete input to less complete input, moving from miminal required inference to maximal inference on the part of the function. Similarly, the structure highlights the flexibility of the function across diverse study designs and input constraints.

### One Sample Cases

```{r}
# 1. Ratio and SE provided (no inference needed)
backcalc_ratios(ratio = 2.5, se = 0.2)

# 2. Ratio and confidence interval provided (infer SE from CI)
backcalc_ratios(ratio = 1.8, ci = c(1.3, 2.5))

# 3. Ratio and test statistic provided (infer SE from statistic)
backcalc_ratios(ratio = 3.0, statistic = 4.0)

# 4. Ratio, test statistic, and df provided (infer SE and p)
backcalc_ratios(ratio = 2.2, statistic = 2.5, df = 29)

# 5. Ratio, test statistic, and sample size (infer SE, df, p, and CI)
backcalc_ratios(ratio = 1.5, statistic = 2.1, n = 40)
```

### Two Sample Cases

```{r}
# 6. Two ratios and SEs provided (no inference needed)
backcalc_ratios(ratio = c(2.5, 1.8), se = c(0.2, 0.1))

# 7. Two ratios, SEs, and dfs provided (Welch-Satterthwaite df calculation)
backcalc_ratios(ratio = c(3.2, 1.9), se = c(0.25, 0.15), df = c(25, 30))

# 8. Two ratios, SE for first group, and CI for the difference (infer second SE and test stats)
backcalc_ratios(ratio = c(2.0, 1.5), se = 0.12, ci = c(1.2, 3.0))

# 9. Two ratios, SE for first group, test statistic and df provided (infer missing SE and p)
backcalc_ratios(ratio = c(2.0, 1.5), se = 0.15, statistic = 3.0, df = 40)

# 10. Two ratios and CI provided (infer SE and all inferential stats)
backcalc_ratios(ratio = c(2.1, 1.7), ci = c(1.05, 3.1))
```

### Insufficient Information Cases

```{r}
# 11. No ratio provided (immediate insufficient info)
backcalc_ratios()

# 12. Ratio provided but no SE, statistic, or CI (insufficient SE)
backcalc_ratios(ratio = 2.3)

# 13. Two-sample ratio vector with SE missing (insufficient info, triggers message)
backcalc_ratios(ratio = c(2.5, 1.9))

# 14. Ratio and p-value provided but no SE, statistic, or CI (insufficient SE)
backcalc_ratios(ratio = 1.8, p = 0.05)

# 15. Ratio with zero or negative value (invalid for log transform, insufficient info)
backcalc_ratios(ratio = c(-1.5, 2.0))
```
