---
title: "ANOVA Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{ANOVA Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## ANOVA Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### Between-Subjects Cases

#### Sherif (1936) — Autokinetic Judgment Conditions

```{r anova_sherif_between}
backcalc_anova(F = 6.84, df1 = 2, df2 = 57, design = "between")
```

Interpretation: The reconstructed between-condition evidence indicates reliable mean separation across conditions, supporting the claim that social framing shifts ambiguous judgments.

#### Zimbardo et al. (1973) — Prison-Role Behavior Index

```{r anova_zimbardo_between}
backcalc_anova(F = 4.21, df1 = 1, df2 = 22, design = "between")
```

Interpretation: The group contrast shows clear evidence, supporting role-internalization accounts in which assigned institutional roles shape behavior.

### Repeated Or Mixed Cases

#### Stroop (1935) — Condition Effect Over Repeated Trials

```{r anova_stroop_within}
backcalc_anova(F = 9.63, df1 = 2, df2 = 62, design = "within", epsilon = 0.92)
```

Interpretation: The within-design effect is strong, supporting the Stroop conclusion that conflict between automatic and controlled processes persists across trials.

#### Latane et al. (1981) — Group-Size By Setting Mixed Design

```{r anova_latane_mixed}
backcalc_anova(F = 3.55, df1 = 2, df2 = 84, design = "mixed")
```

Interpretation: The mixed-design result indicates systematic condition differences, aligning with social-impact models of group presence and size effects.

