---
title: "Coefficients Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{Coefficients Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Coefficients Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### Single Coefficient Cases

#### Thorndike (1904) — Practice To Performance Slope

```{r coeffs_thorndike}
backcalc_coeffs(b = 0.42, se = 0.11, df = 58)
```

Interpretation: The slope is positive with moderate precision, supporting the substantive practice principle that repeated exposure improves performance.

#### Yerkes & Dodson (1908) — Arousal-Performance Slope

```{r coeffs_yerkes_dodson}
backcalc_coeffs(b = -0.31, p = 0.02, df = 44)
```

Interpretation: The coefficient is negative, and the reconstructed evidence supports a non-null slope, supporting the Yerkes-Dodson claim that high arousal can impair performance.

### Standardized Coefficient Cases

#### Cronbach (1951) — Reliability Predictor Weight

```{r coeffs_cronbach_std}
backcalc_coeffs(std_beta = 0.38, se_std = 0.14, df = 62)
```

Interpretation: The standardized coefficient is positive and moderate, indicating a meaningful predictor contribution and reinforcing the practical importance of reliability-related predictors.

#### Meehl (1954) — Criterion Validity Predictor Weight

```{r coeffs_meehl_std}
backcalc_coeffs(b = 1.7, se = 0.55, sd_x = 4.1, sd_y = 9.6, n = 52)
```

Interpretation: The raw effect is positive with moderate uncertainty, and the standardized conversion preserves direction, supporting criterion-validity interpretations.

