---
title: "Coefficients Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Coefficients Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Coefficient Examples

Each section of examples below progresses from more complete input to less complete input, moving from miminal required inference to maximal inference on the part of the function. Similarly, the structure highlights the flexibility of the function across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Unstandardized Beta Cases

```{r}
# 1. Basic: coefficient and SE provided, assume z-test
backcalc_coeffs(b = 0.5, se = 0.1)

# 2. Coefficient and p-value given, with df for t-test; infer SE and t
backcalc_coeffs(b = 1.2, p = 0.03, df = 28)

# 3. Estimate and confidence interval given with df; infer SE and t-statistic
backcalc_coeffs(b = 0.8, ci = c(0.2, 1.4), df = 45)

# 4. Estimate, SE, and sample size given; infer df and CI
backcalc_coeffs(b = -0.7, se = 0.2, n = 50)

# 5. Estimate and test statistic provided directly with df; infer SE and p
backcalc_coeffs(b = 0.9, statistic = 2.3, df = 30)
```

### Standardized Beta and Conversion Cases

```{r}
# 6. Standardized beta and SE_std given; z-test assumed
backcalc_coeffs(std_beta = 0.25, se_std = 0.04)

# 7. Unstandardized beta and SDs given; infer standardized beta and SE_std
backcalc_coeffs(b = 1.1, se = 0.3, sd_x = 2.5, sd_y = 5)

# 8. Standardized beta, p-value, and df given; infer SE_std and t-statistic
backcalc_coeffs(std_beta = 0.3, p = 0.02, df = 25)

# 9. Provide standardized beta, CI, and sample size; infer SE_std and p
backcalc_coeffs(std_beta = 0.4, ci = c(0.1, 0.7), n = 40)

# 10. Standardized beta and statistic given with df; infer SE_std and p
backcalc_coeffs(std_beta = 0.35, statistic = 2.1, df = 29)
```

### Insufficient Information Cases

```{r}
# 11. Only p-value given, no estimate or SE
backcalc_coeffs(p = 0.05)

# 12. Only SE given, no estimate
backcalc_coeffs(se = 0.15)

# 13. Only confidence interval lower bound (invalid length)
backcalc_coeffs(ci = 0.3)

# 14. Only standardized SE given, no standardized beta
backcalc_coeffs(se_std = 0.05)

# 15. Only sample size given, no estimate, SE, or p
backcalc_coeffs(n = 100)
```
