---
title: "Correlations Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{Correlations Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Correlations Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### One Sample Cases

#### Rosenhan (1973) — Confidence And Diagnostic Certainty

```{r corrs_rosenhan}
backcalc_corrs(r = 0.42, n = 48)
```

Interpretation: The positive correlation with moderate sample size indicates meaningful co-movement, supporting the substantive claim that confidence and diagnostic certainty can become tightly coupled.

#### Tolman (1948) — Maze Performance And Trials

```{r corrs_tolman}
backcalc_corrs(r = 0.57, ci = c(0.33, 0.73), n = 36)
```

Interpretation: The correlation is large and its interval remains clearly positive, supporting purposive-learning interpretations linking experience to maze performance.

### Two Sample Cases

#### Maccoby & Jacklin (1974) — Subgroup Correlation Comparison

```{r corrs_maccoby_jacklin_compare}
backcalc_corrs(r = c(0.34, 0.11), n = c(82, 79))
```

Interpretation: The subgroup correlations differ in magnitude, and the comparison supports a directional gap, suggesting the construct relationship varies across populations.

#### Sherif et al. (1961) — Intergroup Context Correlation Shift

```{r corrs_sherif_compare}
backcalc_corrs(r = c(0.46, 0.20), n = c(40, 38))
```

Interpretation: The correlation decreases across contexts, and the reconstructed difference supports attenuation, aligning with accounts that social setting weakens expected trait-behavior coupling.

