---
title: "Means Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{Means Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Means Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### One Sample Cases

#### Loftus & Palmer (1974) — "Smashed" Condition

```{r means_loftus_palmer}
backcalc_means(m = 40.8, se = 1.19, df = 44)
```

Interpretation: Because the estimated mean is clearly positive with moderate uncertainty, the result supports the classic claim that wording can shift eyewitness judgments, implying reconstructive memory processes.

#### Dutton & Aron (1974) — High Bridge Condition

```{r means_dutton_aron}
backcalc_means(m = 2.99, se = 0.268, df = 19)
```

Interpretation: The positive estimate and relatively small uncertainty indicate a stable directional effect, consistent with misattribution of arousal from context to attraction.

### Paired Sample Cases

#### Milgram (1963) — Shock Differences

```{r means_milgram_paired}
backcalc_means(m = 0.15, se = 0.05, df = 39, paired = TRUE)
```

Interpretation: The paired estimate is positive and precise relative to its size, which supports a reliable within-subject shift consistent with classic obedience effects under authority pressure.

#### Haney et al. (1973) — Aggression Scores

```{r means_haney_paired}
backcalc_means(m = 2.0, se = 0.306, df = 23, paired = TRUE)
```

Interpretation: The positive paired effect with moderate uncertainty indicates a meaningful condition-related increase, aligning with the claim that institutional roles can rapidly shape aggressive behavior.

### Two Sample Cases

#### Bandura et al. (1961) — Bobo Doll Study

```{r means_bandura_twosample}
backcalc_means(m = 1.0, se = 0.217, df = 45)
```

Interpretation: The between-group estimate is positive with acceptable precision, supporting the substantive social-learning interpretation that modeled aggression elevates children's aggressive responding.

#### Asch (1951) — Conformity Rates

```{r means_asch_twosample}
backcalc_means(m = 0.32, se = 0.0259, df = 58)
```

Interpretation: The positive estimate paired with very small uncertainty implies a robust group difference, reinforcing the conformity conclusion that majority pressure shifts public judgments.

