---
title: "Medians Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{Medians Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Medians Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### One Sample Cases

#### Ebbinghaus (1885) — Retention Interval Comparison

```{r medians_ebbinghaus}
backcalc_medians(mdn = 36, iqr = 18, n = 28)
```

Interpretation: The positive central estimate with nontrivial dispersion indicates a stable retention level but broad spread, supporting the substantive conclusion that memory changes substantially over delay.

#### Rosenthal & Jacobson (1968) — Gain Score Median

```{r medians_rosenthal_jacobson}
backcalc_medians(mdn = 5.0, mad = 2.7, n = 24)
```

Interpretation: The positive median gain and moderate uncertainty support a directional improvement pattern consistent with expectancy-based classroom effects.

### Paired Sample Cases

#### Stroop (1935) — Interference Condition Difference Scores

```{r medians_stroop_paired}
backcalc_medians(mdn = 7.0, iqr = 9.5, n = 32, paired = TRUE)
```

Interpretation: The paired median shift with appreciable spread indicates a consistent directional interference effect, matching the Stroop claim that automatic reading competes with controlled color naming.

#### Tversky & Kahneman (1974) — Judgment Shift Scores

```{r medians_tversky_kahneman_paired}
backcalc_medians(mdn = 4.0, range = 20, n = 30, paired = TRUE)
```

Interpretation: The positive paired shift alongside broad uncertainty still supports the directional claim predicted by anchoring-and-adjustment accounts.

### Two Sample Cases

#### Festinger & Carlsmith (1959) — Dissonance Condition Ratings

```{r medians_festinger_carlsmith}
backcalc_medians(mdn = c(7.0, 5.5), iqr = c(2.4, 2.8), n = c(20, 20))
```

Interpretation: The median contrast with moderate dispersion in both groups supports a directional between-condition difference aligned with cognitive dissonance interpretations.

#### Mischel et al. (1972) — Delay-Choice Outcomes

```{r medians_mischel_twosample}
backcalc_medians(mdn = c(15, 9), mad = c(4, 5), n = c(26, 24))
```

Interpretation: The sizable median gap, despite group variability, indicates a meaningful condition difference consistent with delay-of-gratification accounts of self-control.

