---
title: "Medians Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Medians Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Medians Examples

Each section of examples below progresses from more complete input to less complete input, moving from miminal required inference to maximal inference on the part of the function. Similarly, the structure highlights the flexibility of the function across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### One Sample Cases

```{r}
# 1.  Median, IQR, and sample size
backcalc_medians(m = 50, iqr = 20, n = 30)

# 2.  Median, MAD, and sample size
backcalc_medians(m = 48, mad = 12, n = 25)

# 3.  Median, IQR, paired design
backcalc_medians(m = 42, iqr = 15, n = 20, paired = TRUE)

# 4.  Median, MAD, one-sided test
backcalc_medians(m = 55, mad = 10, n = 40, one_sided = TRUE)

# 5. median + MAD + n, no paired, no one-sided
backcalc_medians(m = 55, range = 30, n = 20)
```

### Two Sample Cases

```{r}
# 6.  Group medians, IQR, and sample size
backcalc_medians(m = c(60, 50), iqr = 20, n = 30)

# 7.  Group medians, MAD, and sample size
backcalc_medians(m = c(75, 68), mad = 9, n = 40)

# 8.  Paired medians, IQR, and n
backcalc_medians(m = c(45, 40), iqr = 10, n = 20, paired = TRUE)

# 9.  Group medians, IQR, n, one-sided
backcalc_medians(m = c(82, 78), iqr = 12, n = 35, one_sided = TRUE)

# 10. two medians, two MADs, two sample sizes (no IQR used here)
backcalc_medians(m = c(92, 85), mad = c(7, 10), n = c(25, 28))
```

### Insufficient Information Cases

```{r}
# 11. Only IQR provided
backcalc_medians(iqr = 10)

# 12. Only MAD provided
backcalc_medians(mad = 5)

# 13. Only sample size provided
backcalc_medians(n = 30)

# 14. Median provided, no n or spread
backcalc_medians(m = 50)

# 15. Medians and sample size, but no dispersion
backcalc_medians(m = c(52, 49), n = 30)
```
