---
title: "Proportions Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{Proportions Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Proportions Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### One Sample Cases

#### Milgram (1963) — Baseline Obedience Rate

```{r props_milgram_baseline}
backcalc_props(x = 26, n = 40)
```

Interpretation: The observed proportion is high, and its reconstructed interval remains well above trivial levels, supporting Milgram's substantive conclusion that many participants complied under authority pressure.

#### Darley & Batson (1973) — Helping In The Seminary Study

```{r props_darley_batson}
backcalc_props(x = 10, n = 40)
```

Interpretation: The helping proportion is low, and the uncertainty band stays far from ceiling behavior, supporting the situationist interpretation that context can suppress prosocial action.

### Two Sample Cases

#### Milgram (1963) — Baseline Vs. Touch-Proximity Conditions

```{r props_milgram_condition_compare}
backcalc_props(x = c(26, 12), n = c(40, 40))
```

Interpretation: The two-group difference in proportions is large and directionally consistent, supporting the claim that situational manipulations of social distance can materially reduce obedience.

#### Latane & Darley (1968) — Seizure Study, Alone Vs. Group Condition

```{r props_latane_darley_compare}
backcalc_props(x = c(11, 4), n = c(13, 13))
```

Interpretation: The substantial proportion gap indicates a strong directional effect, substantiating the bystander-effect claim that shared responsibility diffuses intervention.

