---
title: "Ratios Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{Ratios Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Ratios Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### One Sample Cases

#### Weber (1834) — Just-Noticeable Difference Ratio Summaries

```{r ratios_weber}
backcalc_ratios(ratio = 1.32, se = 0.09, df = 29)
```

Interpretation: The ratio estimate exceeds one and is reasonably precise, which supports the Weberian claim that sensitivity tracks proportional, not absolute, change.

#### Fechner (1860) — Psychophysical Ratio Estimate

```{r ratios_fechner}
backcalc_ratios(ratio = 1.18, ci = c(1.05, 1.33), n = 41)
```

Interpretation: The ratio remains above one with an interval that also stays above one, supporting Fechner-style scaling in which perceived intensity grows systematically with stimulus magnitude.

### Two Sample Cases

#### Stevens (1957) — Magnitude Estimation By Task

```{r ratios_stevens_compare}
backcalc_ratios(ratio = c(1.48, 1.21), se = c(0.11, 0.10), df = c(22, 24))
```

Interpretation: The first context shows a larger ratio, and combined uncertainty information supports a reliable directional contrast, consistent with context-dependent judgment scaling.

#### Shepard (1967) — Generalization Ratio By Context

```{r ratios_shepard_compare}
backcalc_ratios(ratio = c(1.61, 1.27), ci = c(1.08, 1.79), df = 30)
```

Interpretation: The comparison of ratios, together with interval-based uncertainty, supports a positive contextual shift consistent with generalization accounts of transfer strength.

