---
title: "Regression Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{Regression Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Regression Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse input constraints for multiple regression coefficients.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### Multiple Regression Cases

#### Coleman et al. (1966) — School Outcomes Model

```{r multreg_coleman}
backcalc_multreg(
  intercept = 2.1,
  intercept_se = 0.6,
  b = c(0.45, -0.28, 0.33),
  se = c(0.12, 0.10, 0.11),
  n = 120
)
```

Interpretation: The model includes both positive and negative coefficients with moderate uncertainty, supporting a multicausal substantive account where predictors influence outcomes in different directions.

#### Jencks et al. (1972) — Educational Attainment Model

```{r multreg_jencks}
backcalc_multreg(
  b = c(0.52, 0.19, -0.14, 0.27),
  p = c(0.001, 0.04, 0.09, 0.02),
  n = 150
)
```

Interpretation: The evidence pattern indicates several predictors with clearer support and one weaker effect, supporting the claim that attainment is jointly determined but unequally weighted across predictors.

