---
title: "Multiple Regression Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Multiple Regression Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Multiple Regression Examples

Each section of examples below progresses from more complete input to less complete input, moving from minimal required inference to maximal inference on the part of the function. Similarly, the structure highlights the flexibility of the function across diverse input constraints for multiple regression coefficients.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### Unstandardized Coefficients Cases

```{r}
# 1. Full info: unstandardized coefficients, standard errors, and df
backcalc_multreg(
  intercept = 3.2, intercept_se = 0.5,
  b = c(0.4, 0.8), se = c(0.1, 0.15),
  df = 50
)

# 2. Unstandardized coefficients, SEs, and standard deviations; infer standardized coefficients
backcalc_multreg(
  intercept = 1.8, intercept_se = 0.4,
  b = c(0.7, 1.2, 0.3),
  se = c(0.15, 0.2, 0.08),
  sd_x = c(1.5, 2.2, 0.8),
  sd_y = 3,
  n = 110
)

# 3. Unstandardized coefficients with SEs and sample size; infer df and t-test
backcalc_multreg(
  intercept = 3.1, intercept_se = 0.55,
  b = c(0.6, 0.8),
  se = c(0.15, 0.12),
  n = 85
)

# 4. Unstandardized coefficients with SEs and test statistics; no df, use z-test
backcalc_multreg(
  intercept = 3.1, intercept_se = 0.55,
  b = c(0.6, 0.8),
  se = c(0.15, 0.12),
  statistic = c(4, 6)
)

# 5. Unstandardized coefficients and p-values given; infer SEs and test statistics
backcalc_multreg(
  intercept = 2.4, intercept_se = 0.35,
  b = c(0.4, 0.7),
  p = c(0.04, 0.01),
  n = 85
)
```

### Standardized Coefficients Cases

```{r}
# 6. Standardized betas with SEs and sample size
backcalc_multreg(
  intercept = 3.2, intercept_se = 0.5,
  std_beta = c(0.3, 0.5), se_std = c(0.1, 0.12),
  n = 100
)

# 7. Standardized betas with SEs and degrees of freedom
backcalc_multreg(
  intercept = 2.5, intercept_se = 0.3,
  std_beta = c(0.25, 0.55, 0.1),
  se_std = c(0.07, 0.1, 0.05),
  df = 90
)

# 8. Unstandardized coefficients with SEs and standard deviations; infer standardized betas
backcalc_multreg(
  intercept = 2.0, intercept_se = 0.6,
  b = c(1.1, 0.5), se = c(0.3, 0.2),
  sd_x = c(2.5, 3), sd_y = 5,
  n = 120
)

# 9. Standardized betas with missing SEs; use unstandardized input for approximation
backcalc_multreg(
  intercept = 3.0, intercept_se = 0.45,
  std_beta = c(0.3, NA, 0.5),
  se_std = c(0.1, NA, 0.12),
  b = c(NA, 0.4, NA),
  se = c(NA, 0.15, NA),
  sd_x = c(2, 3, 2.5),
  sd_y = 5,
  n = 130
)

# 10. Intercept with confidence intervals for predictors and sample size; infer SEs
backcalc_multreg(
  intercept = 4.5, intercept_se = 0.4,
  ci = list(c(0.2, 0.8), c(0.1, 0.9)),
  n = 80
)
```

### Insufficient Information Cases

```{r}
# 11. Predictors with no estimates and no confidence intervals
backcalc_multreg(
  intercept = 2.0, intercept_se = 0.4,
  se = c(0.1, 0.15),
  n = 100
)

# 12. Standardized betas provided, but SEs missing with no sample size or df
backcalc_multreg(
  intercept = 1.8, intercept_se = 0.25,
  std_beta = c(0.2, 0.5, 0.3)
)

# 13. Intercept with unstandardized predictor, missing SE for second predictor
backcalc_multreg(
  intercept = 1.5, intercept_se = 0.25,
  b = c(0.5, NA), se = c(0.1, NA), p = c(NA, 0.05),
  n = 150
)

# 14. Intercept with predictor estimates only, missing SE information
backcalc_multreg(
  intercept = 2.0, intercept_se = 0.4,
  b = c(0.5, 0.8)
)

# 15. Intercept with predictor p-values only, no estimates or df provided
backcalc_multreg(
  intercept = 1.5, intercept_se = 0.3,
  p = c(0.05, 0.01)
)
```
