---
title: "Standardized Mean Differences Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Standardized Mean Differences Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Standardized Mean Differences Examples

Each section of examples below progresses from more complete input to less complete input, moving from minimal required inference to maximal inference on the part of the function. Similarly, the structure highlights the flexibility of the function across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### One Sample Cases

```{r}
# 1. Cohen's d from mean difference, SD, and sample size (minimal inference)
backcalc_standard(m = 2.5, sd = 4, n = 25)

# 2. Hedges' g from one-sample input (bias-corrected d)
backcalc_standard(m = 1.5, sd = 3, n = 30, type = "g")

# 3. One-sample effect size from t-statistic and sample size
backcalc_standard(statistic = 2.5, n = 50)

# 4. One-sample estimate from CI midpoint plus sample size
backcalc_standard(ci_d = c(0.2, 0.8), n = 40)

# 5. Directly supplied d with sample size to obtain SE and CI
backcalc_standard(d = 0.45, n = 60)
```

### Two and Paired Sample Cases

```{r}
# 6. Two-sample Cohen's d from means, SDs, and sample sizes
backcalc_standard(m = c(15, 12), sd = c(4, 5), n = c(40, 35))

# 7. Two-sample Hedges' g with unequal group sizes
backcalc_standard(m = c(20, 18), sd = c(3, 3), n = c(50, 20), type = "g")

# 8. Two-sample Glass's delta using group 2 as control SD
backcalc_standard(m = c(15, 12), sd = c(4, 5), n = c(40, 35), type = "delta", control_sd = 2)

# 9. Two-sample effect size from t-statistic with SDs and group sample sizes
backcalc_standard(statistic = 3.0, sd = c(4, 5), n = c(40, 40))

# 10. Paired-sample Cohen's d from mean difference, SD, and n
backcalc_standard(m = 1.2, sd = 2.5, n = 30, paired = TRUE)
```

### Insufficient Information Cases

```{r}
# 11. Sample size only, no effect size, mean difference, or statistic
backcalc_standard(n = 40)

# 12. SD and sample size provided, but no mean difference or effect size
backcalc_standard(sd = 3, n = 35)

# 13. Test statistic provided without sample size
backcalc_standard(statistic = 2.1)

# 14. P-value and sample size provided, but no effect size or statistic
backcalc_standard(p = 0.03, n = 45)

# 15. Mean difference only, missing SD and effect size
backcalc_standard(m = 1.8)
```
