---
title: "Standardized Mean Differences Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Standardized Mean Differences Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Standardized Mean Differences Examples

Each section of examples below progresses from more complete input to less complete input, moving from miminal required inference to maximal inference on the part of the function. Similarly, the structure highlights the flexibility of the function across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### One Sample Cases

```{r}
# 1. Cohen's d from mean difference, SD, and sample size (minimal inference)
backcalc_standardized_means(m = 2.5, sd = 4, n = 25)

# 2. Cohen's d with larger sample (more precision)
backcalc_standardized_means(m = 1.5, sd = 3, n = 100)
```

### Two Sample Cases

```{r}
# 3. Cohen's d from two group means, SDs, and sample sizes
backcalc_standardized_means(m = c(15, 12), sd = c(4, 5), n = c(40, 35))

# 4. Cohen's d for unequal group sizes
backcalc_standardized_means(m = c(20, 18), sd = c(3, 3), n = c(50, 20))
```

### Different Effect Size Types

```{r}
# 5. Hedges' g (bias-corrected version of Cohen's d)
backcalc_standardized_means(m = c(15, 12), sd = c(4, 5), n = c(40, 35), type = "g")

# 6. Hedges' g with small sample
backcalc_standardized_means(m = c(10, 8), sd = c(2, 2), n = c(10, 10), type = "g")

# 7. Glass's delta (control group SD)
backcalc_standardized_means(m = c(15, 12), sd = c(4, 5), n = c(40, 35), type = "delta", control_sd = 2)
```

### Backcalculation from Test Statistics

```{r}
# 8. Effect size from t-statistic (one-sample)
backcalc_standardized_means(statistic = 2.5, n = 50)

# 9. Two-sample effect size from t-statistic
backcalc_standardized_means(statistic = 3.0, n = c(40, 40))
```

### Paired Designs

```{r}
# 10. Paired samples Cohen's d
backcalc_standardized_means(m = 1.2, sd = 2.5, n = 30, paired = TRUE)
```

### Insufficient Information Cases

```{r}
# 11. Insufficient input (only effect size, no SE or CI information)
backcalc_standardized_means(d = 0.5)
```
