---
title: "Standardized Effects Published Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\\VignetteIndexEntry{Standardized Effects Published Cases}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
# suppress warnings and messages in knitted output.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(backcalc)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/backcalc")
}
library(backcalc)
```

## Standardized Effects Published Cases

The sections below move from one published study to another, showing how the package can be used to interpret research findings across diverse study designs and input constraints.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 1)
```

---

### One Sample Cases

#### Triplett (1898) — Social Facilitation Effect Size

```{r standard_triplett}
backcalc_standard(m = 1.8, sd = 4.9, n = 40, type = "d")
```

Interpretation: The standardized effect is positive, indicating nontrivial directional change and supporting the social-facilitation claim that coaction can enhance performance.

#### Lewin et al. (1939) — Leadership Climate Effect Size

```{r standard_lewin}
backcalc_standard(statistic = 2.35, n = 36, type = "g")
```

Interpretation: The reconstructed Hedges g remains positive after small-sample correction, consistent with leadership-climate theories linking social climate to behavior change.

### Two Sample Cases

#### Bandura et al. (1961) — Aggression Score Contrast

```{r standard_bandura}
backcalc_standard(m = c(1.00, 0.46), sd = c(0.95, 0.89), n = c(24, 24), type = "d")
```

Interpretation: The between-group standardized difference is positive, indicating a practical effect size that reinforces social-learning interpretations of generalized aggression.

#### Darley & Latane (1968) — Helping Latency Contrast

```{r standard_darley_latane}
backcalc_standard(m = c(38.2, 61.5), sd = c(20.4, 27.6), n = c(18, 18), type = "g")
```

Interpretation: The standardized contrast is substantial, supporting bystander-effect mechanisms in which social context alters urgency and helping latency.

